Visualization tool for comparison of mutations in protein simulations

### 2017-06-27 paper/paper.tex
cleaned

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Example of IEEEtran.cls, adapted for Sibgrapi 2015}

@@

\iffinal
  \author{%
    \IEEEauthorblockN{Bruno Iochins Grisci}
    \IEEEauthorblockA{%
      line 1 (of Affiliation): Instituto de Informatica\\
      line 2: UFRGS\\
      line 3: Porto Alegre, Brazil\\
      line 4: Email:  \href{mailto:bigrisci@inf.ufrgs.br}{bigrisci@inf.ufrgs.br}}
  \and
    \IEEEauthorblockN{Authors Name/s per 2nd Affiliation}
    \IEEEauthorblockA{%
      line 1 (of Affiliation): dept. name of organization\\
      line 2: name of organization, acronyms acceptable\\
      line 3: City, Country\\
      line 4: }
  }
\else
  \author{Sibgrapi paper ID: \jemsid \\ }
\fi

@@

%==========================================
%==========================================

@@

%------------------------------------------------------------------------- 
\paragraph*{Contributions}
%
This paper proposes a different approach to overcome those difficulties. By introducing and adapting those techniques to this context, we achieve significant improvements on the recent results. In particular, our method can handle this kind of data, and reduces the resource requirements. In our experiments, we evaluate a gain of $xx\%$ and could observe several interesting results that validate and delimit our approach.

%------------------------------------------------------------------------- 
\subsection{Related work}
%
We can roughly classify the approaches used for our application in three categories: first category, second category, and last category.\\
Approaches in the first category were introduced by Pierre~\cite{Sibgrapi2015} using this and that techniques.

\subimages[htb]{Technique overview}{overview}{%
  \subimage[First step]{.31}{sibgrapi}%
  \subimage[Second step]{.31}{sibgrapi}%
  \subimage[Result]{.31}{sibgrapi}%
}
%------------------------------------------------------------------------- 
\subsection{Technique overview}
%
In order to produce this application, we start with this processing, followed by this technique. In order to cope with this challenge, we introduce this formulation to produce this intermediate result. The formulation leads to this type of system, which is efficiently solved by adapting this technique. The final result is produced by this transform. The whole process is schematized in \figref{overview}.

@@

%------------------------------------------------------------------------- 
\subsection{Important concept}
%
An \emph{important concept} is a type of object:
\begin{definition}[Important concept]
Given this and that, an object $X$ is an important concept if it respects the following properties\ldots{}
\end{definition}

%------------------------------------------------------------------------- 
\subsection{Usual adaptation}
%
This concept has been used for applications similar to ours~\cite{Sibgrapi2015}, using the following formulation\ldots{}

%==========================================
\section{New technique or technique adaptation}
\label{sec:technique}
%
Our technique aims at obtaining that result. It particularly suits to the problem since it is formulated as\ldots{}

%------------------------------------------------------------------------- 
\subsection{Formulation}

%------------------------------------------------------------------------- 
\subsection{Solution}

%------------------------------------------------------------------------- 
\subsection{Initialization and tuning}

%==========================================
\section{Implementation}
%
In order to reduce the resources needed for our method, we use the following implementation strategy.

%------------------------------------------------------------------------- 
\subsection{Solver}

%------------------------------------------------------------------------- 
\subsection{Result display}

@@

%------------------------------------------------------------------------- 
\paragraph*{First experiment}
%
The first experiment checks this aspect of our method on perfect examples.

%------------------------------------------------------------------------- 
\paragraph*{Second experiment}
%
The second experiment checks the speedup obtained by the implementation strategy compared to previous technique~\cite{Sibgrapi2015}.

%------------------------------------------------------------------------- 
\paragraph*{Third experiment}
%
The last experiment test our method on real data.

@@

%------------------------------------------------------------------------- 
\subsection{Limitation}
%
As mentioned in Section~\ref{sec:technique}, we expect our method to suit better this kind of data. On the other kind, this particularity does not fit into our formulation for this and that reason. Indeed, this can be observed in the results of \figref{quality}. 
We plan to improve for that kind of data in future work. However, our technique performed well on this data, which does not respect our condition, since this other aspect reduced the negative impact of its characteristic.

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Visualization tool for comparison of mutations in protein simulations}

@@

\iffinal
  \author{%
    \IEEEauthorblockN{Bruno Iochins Grisci}
    \IEEEauthorblockA{%
      Instituto de Informatica\\
      UFRGS\\
      Porto Alegre, Brazil\\
      Email:  \href{mailto:bigrisci@inf.ufrgs.br}{bigrisci@inf.ufrgs.br}}
  }
\else
  \author{Sibgrapi paper ID: \jemsid \\ }
\fi

@@

%==========================================
%==========================================
 %1) Introdução (motivação para o trabalho, objetivos e resultados esperados), 2) Caracterização dos dados e problema/questões que a visualização pretende responder, 3) Descrição da técnica de visualização desenvolvida (incluir aqui informação sobre a implementação, biblioteca ou ferramenta utilizada), 4) Resultados (exemplos de uso), 5) Conclusões. Não há limite de páginas, mas o razoável é de 8 a 12 páginas no máximo.

@@

\subsection{Related work}
%
We can roughly classify the approaches used for our application in three categories: first category, second category, and last category.\\
Approaches in the first category were introduced by Pierre~\cite{Sibgrapi2015} using this and that techniques.

\subimages[htb]{Technique overview}{overview}{%
  \subimage[First step]{.31}{sibgrapi}%
  \subimage[Second step]{.31}{sibgrapi}%
  \subimage[Result]{.31}{sibgrapi}%
}

%==========================================
\section{Data characterization}

\subsection{Data dimensions}

\paragraph*{DSSP}
%
The first experiment checks this aspect of our method on perfect examples.

\paragraph*{SASA}
%
The first experiment checks this aspect of our method on perfect examples.

\paragraph*{GYRATE}
%
The first experiment checks this aspect of our method on perfect examples.

\paragraph*{ENERGY}
%
The first experiment checks this aspect of our method on perfect examples.

\paragraph*{RMSF}
%
The first experiment checks this aspect of our method on perfect examples.

@@

%------------------------------------------------------------------------- 
\section{Technique overview}
%
In order to produce this application, we start with this processing, followed by this technique. In order to cope with this challenge, we introduce this formulation to produce this intermediate result. The formulation leads to this type of system, which is efficiently solved by adapting this technique. The final result is produced by this transform. The whole process is schematized in \figref{overview}.

\subsection{Grid}
\paragraph*{Item highlighting}
\paragraph*{Item selection}

\subsection{Parallel Coordinates}

\paragraph*{Axis brushing}
\paragraph*{Axis sorting}
\paragraph*{Axis reordering}
\paragraph*{Recoloring by axis selection}

\subsection{Radar Plot}
\paragraph*{Item highlighting}

\subsection{Slider}

@@

@@

%------------------------------------------------------------------------- 
\subsection{Future work}
%
As mentioned in Section~\ref{sec:technique}, we expect our method to suit better this kind of data. On the other kind, this particularity does not fit into our formulation for this and that reason. Indeed, this can be observed in the results of \figref{quality}. 
We plan to improve for that kind of data in future work. However, our technique performed well on this data, which does not respect our condition, since this other aspect reduced the negative impact of its characteristic.
